\sloppy \section{Reflection Perspective}
\byline{Andreas Schiøtt, Sebastian Holt Svendsen}

\subsection{Evolution and Refactoring}

Our initial implementation of CI/CD pipelines ran concurrently: a push would trigger  
deployment before its CI run had finished, so failing build could reach production silently. 
We fixed this by gating CD on a successful CI run, and later added caching to speed up the End-to-End 
tests, which had been a bottleneck in the process. \\
In early iterations we did not cull old containers on deployment. The resulting CPU pressure 
was first visible through our monitoring stack, which then became a crucial diagnostic tool. 
Monitoring and logging initially ran on the same droplet as the application, a single point of failure that could blind 
us at the worst moment, so we moved them onto a dedicated droplet, a decision that proved fortunate 
when that droplet was later compromised (see next paragraph), as it limited the blast radius and 
kept the application running.

% What were the biggest challenges when evolving the codebase?
% How did you handle breaking changes, migrations, etc.?
% Link to relevant commits, issues, or PRs as evidence.

\paragraph{Hacking incident.} \label{sec:hacking-incident} On 2026-04-21 we discovered that our monitoring droplet had been compromised three 
days earlier: a brute-force SSH scanning campaign, ongoing since 2026-04-19, had culminated in 
the \texttt{preprod-deploy} key being used for root access from four Azure IPs. The attacker 
deployed a cryptominer disguised as \texttt{/tmp/mysql}, created a fake \texttt{dnsmasq} user 
for persistence, and started a rogue \texttt{chirp-postgres} container. Ironically the compromise 
was discovered not through our monitoring stack but because of it, the droplet was unresponsive and 
pinned at 100\% CPU, leading to a manual investigation. Because root had been obtained directly 
via the leaked key, the host could not be salvaged. We destroyed and rebuilt it, restricting SSH 
access via UFW to our own IPs. The full forensic timeline is preserved in \texttt{security-incident-ie-BITCOIN-MINE.md}.

\paragraph{Architectual refactor.} The system underwent multiple major architectural refactors over the semester, 
from a locally hosted single-container setup, to a Dockerised application using  SQLite, to a DigitalOcean mangaged PostgreSQL,
and finally to a Docker Swarm stack with replicated app instances behind a load-balanced floatin IP.
Each step was forced by a hard limit of the previous one: SQLite's concurrent write limit, single 
host failure modes that took the whole system down, and the need for rolling updates without downtime.
\\
Across these refactors the common thread was operational visibility, every significant improvement 
to the system was the response to a bottleneck or failure discovered either manually or through 
monitoring.
% What was hard to operate?
% Incidents, outages, on-call situations?
% What tooling or practices helped most?
% Link to relevant issues/tickets.

\subsection{Maintenance}
\label{sec:maintenance}
\noindent We did not implement an alerting system, which left a critical observability gap: 
the production environment could fail without anyone knowing until we manually checked. 
The consequences of this were most evident in the security incident described in \cref{sec:hacking-incident}. 
Implementing an alerting system (at minimum Grafana alerts on uptime, CPU saturation, and 
authentication failures) would be the highest priority if we continued operating the system.
Another instructive incident was self-inflicted. To resolve auth cookies being silently invalidated 
when load-balanced across replicas, we added \texttt{AddDataProtection().PersistKeysToStackExchangeRedis(...)} in 
\texttt{Program.cs}. The fix introduced a new failure mode: \texttt{ConnectionMultiplexer.Connect()} is 
blocking and eager, so the entire application failed to start if Redis was momentarily unavailable. 
This broke production on first deploy and our E2E test job (which had no Redis instance). We resolved it by 
adding \texttt{abortConnect=false} to the connection string and adding Redis to the E2E workflow. The lesson 
is that fixes depending on additional infrastructure must be tested against that infrastructure being absent.
Both incidents share the same shape: failures detectable only after the fact, because we built observability 
for diagnosis but not for prevention. Closing the alerting gap and tightening test coverage 
of new infrastructure dependencies would be the highest maintenance priorities.



% How did you keep dependencies up-to-date?
% How did you handle technical debt?
% What would you do differently?

\subsection{DevOps Style of Work}
Compared to previous software projects, our development process was substantially more iterative 
and incremental, with continuous integration and delivery as the default rather than an afterthought. 
The most consequential shift was treating observability as a first-class feature. We built monitoring and
logging early, and tried using them a our primary feedback loop. This habit has carried over into 
our other projects and courses. \\
When it comes to working DevOps style, a DevOps team is most effective when ownership, on call responsibility, 
and review duties are distributed across all members. Ours was not. 
\\
Of our five-person group, two of us carried the substantive work for the full semester. The others didn't commit 
much code, take branches, nor return to tasks taken on. This was not a deliberate decision, but rather an unfortunate outcome
of the group dynamics. Some of this we own: in the first weeks we moved quickly and likely raised the bar for 
participation, probably higher than what was inclusivem, without doin the team-formation work (shared expectations, paired 
tasks, defined responsibilities, etc.) that would have made on-ramping possible. \\
The operational cost was real, a bus-factor of two on every piece of infrastructure, the missing 
alerting in \cref{sec:maintenance}


Much more iterative and incremental development process, with a focus on continuous integration and delivery. 
with a larger focus on introspection and adaption to feedback from monitoring and logging, which allowed us to detect and fix issues in production.



This way of working has a made a large impact on our development process and has changed our approch to software development in our other projects and courses. 

% What did you do differently compared to previous software projects?
% What worked well and what did not?
