\section{Use of Generative AI}
\byline{Andreas Schiøtt, Sebastian Holt Svendsen}

% ITU's generative AI guidelines apply. State:
%   1. Which tools were used (ChatGPT, GitHub Copilot, Claude, etc.)
%   2. For which tasks they were used
%   3. How they supported or hindered your work process

% Example structure:

\subsection{Tools Used}
\begin{itemize}                                                                                                                            
    \item Claude / Claude Code(CLI) For Brainstorming, debugging, Understanding course material, code generation, documentation, code reviews/Refactoring, process improvement suggestions.        
    \item ChatGPT (OpenAI) For Brainstorming, debugging, Understanding course material, code generation, documentation, code reviews/Refactoring, process improvement suggestions.
    \item GitHub Copilot for code suggestions and autocompletion                                                               
\end{itemize} 

\subsection{Impact on Work Process}

\subsubsection{Supported}
It helped us understand course material and concepts better by providing explanations and examples / deepening the explanations from the lectures/course material.
able to get less stuck on problems, and get suggestions for how to solve them, which sped up development. 
helped  with code generation for ci/cd pipelines, dockerfiles, and other boilerplate code. 

\subsubsection{Hindered}
As mentioned earlier, we have been 2 people working on the project, this resulted in us being behind on the project, which meant that the use of generative AI could sometimes could become a crutch to catch up.

\\

\noindent To get value of the use of generative AI had to give alot of context to get usefull suggestions / answers /avoid hallucinations which made output useless. This has been helped by the use of CLI based tools like Claude Code/ Codex which could take the context from the codebase.

% Briefly reflect: did AI speed up development, introduce bugs,
% reduce learning, improve code quality?
% Be honest about limitations as well as benefits.
